Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-09-23 doc/LinksToDAG.tex
changed the sample parses to be displayed. 2 short and 1 long for the paper.
increased the margin at the top, in order to accomodate the (hidden) author space
added a line adding in a second long parse. But commented it out.
mentioned that conll parses are gold - is that correct?
increased the size of the sample link analysis table to put in the paper.
updated the descriptions in figure1 and in the appendix about the parse visualizations making every multiheaded link orange.

% \author{Juneki Hong and Jason Eisner\\
%   Department of Computer Science \\
%   Johns Hopkins University \\
%   Baltimore, MD 21218, USA \\ 
%   {\tt \{juneki,jason\}@cs.jhu.edu} \\
% }

@@

\setlength\titlebox{3cm}    % Expanding the titlebox

@@

@@

\begin{figure*}[ht!]
  \vspace{-6pt}
  \centering
  \input{figure/sentences.tikz}
  \input{figure/sample_parses.tikz}
  \caption{\small The blue upper edges show CoNLL dependency parses; the red lower edges show our oriented version of the link grammar parses. Edges are shown as dotted lines if they appear only in one parse; these are highlighted in orange if the child has multiple parents.  Edges that appear in both parses are solid lines, drawn thicker if the directions do not match.  Vertical edges have parent 0.  For 100 example parses, see Appendix~\ref{app:parses} at \url{http://tidyurl.com/LinksToDAG_supplement}.}
  \label{fig:parses}
  \vspace{-6pt}
\end{figure*}

@@

Edges are shown as dotted lines if they appear only in one parse and not in the other.  Such edges are highlighted in orange if the child has multiple parents.

>>>>

%\author{Juneki Hong and Jason Eisner\\
%   Department of Computer Science \\
%   Johns Hopkins University \\
%   Baltimore, MD 21218, USA \\ 
%   {\tt \{juneki,jason\}@cs.jhu.edu} \\
%}

@@

\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

% 
% \begin{figure*}[ht!]
%   \vspace{-6pt}
%   \centering
%   \input{figure/sample_parses.tikz}
%   \vspace{-6pt}
% \end{figure*}

@@

\begin{figure*}[ht!]
  \vspace{-6pt}
  \centering
  \input{figure/sentences.tikz}
  \input{figure/long_parses.tikz}
  %\input{figure/long_parse2.tikz}
  \caption{\small The blue upper edges show CoNLL gold dependency parses; the red lower edges show our oriented version of the link grammar parses. Edges are shown as dotted lines if they appear only in one parse. Edges are highlighted in orange if the child has multiple parents.  Edges that appear in both parses are solid lines, drawn thicker if the directions do not match.  Vertical edges have parent 0.  For 100 example parses, see Appendix~\ref{app:parses} at \url{http://tidyurl.com/LinksToDAG_supplement}.}
  \label{fig:parses}
  \vspace{-6pt}
\end{figure*}

@@

Edges are shown as dotted lines if they appear only in one parse and not in the other.

Edges are highlighted in orange if the child has multiple parents.
